comgen-outline

### 2017-06-24 paper/comgen-paper.Rmd
replace manipulation check regression with bayesian CIs, calculate in line

As a manipulation check, the first author assigned an \emph{a priori} truth-judgment (true/false/indeterminate) to each stimulus item.
This was a significant predictor of the empirical truth judgments: true generics were significantly more likely to be agreed with than the indeterminate generics ($\beta = 3.14; SE = 0.15; z = 21.5$), as revealed by a mixed-effect logistic regression with random by-participant effects of intercept.
Indeterminate generics were agreed with \emph{less} likely than chance ($\beta = -0.49; SE = 0.09; z = -5.3$) but significantly more than false generics ($\beta = 2.09; SE = 0.14; z = 14.5$).

In addition to these categorical differences between our thirty generic statements, we find a contiuum of endorsement values (Figure \ref{fig:generic-endorsement}).
Such a continuum of judgments is evidence against any theory that only predicts whether a generic statement is true or false.
Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, unendorsed completely, and all shades in between.

>>>>

```{r generic-endorsement-manipulationcheck}
# MHT's truth judgments of sentences
# t --> true; f --> false; i --> indeterminate/uncertain
all.sentences <- list("Cardinals are red." = "t",
 "Ducks have wings." = "t",
 "Kangaroos have pouches." = "t",
 "Kangaroos have spots." = "f",
 "Leopards are juvenile." = "i",
 "Leopards have spots." = "t",
 "Leopards have wings." = "f",
 "Lions are male." = "i",
 "Lions have manes." = "t",
 "Lions lay eggs." = "f",
 "Mosquitos attack swimmers." = "i",
 "Mosquitos carry malaria." = "t",
 "Mosquitos dont carry malaria." = "f",
 "Peacocks dont have beautiful feathers." = "f",
 "Peacocks have beautiful feathers." = "t",
 "Robins are female." = "i",
 "Robins carry malaria." = "f",
 "Robins lay eggs." = "t",
 "Sharks are white." = "i",
 "Sharks attack swimmers." = "t",
 "Sharks dont attack swimmers." = "f",
 "Sharks have manes." = "f",
 "Sharks lay eggs." = "i",
 "Swans are full-grown." = "i",
 "Swans are white." = "t",
 "Ticks carry Lyme disease." = "t",
 "Ticks dont carry Lyme disease."= "f",
 "Tigers dont eat people."= "f",
 "Tigers eat people." = "t",
 "Tigers have pouches."= "f")

mht.truth.judgments <- data.frame(sentence = names(all.sentences),
           truth_judgment = as.vector(unlist(all.sentences)))

d.gen.endorse.manipulation.check.bayes <- left_join(
  left_join(
    d.gen.endorse, 
    d.gen.endorse.catch %>% select(workerid, pass)
    ),
  mht.truth.judgments ) %>%
  filter(pass == 1) %>%
  rowwise() %>%
  mutate(response = ifelse(response == "agree-key", 1, 0),
         sentence = gsub('&quotechar', '', sentence),
         sentence = gsub('lyme', 'Lyme', sentence)) %>%
  group_by(truth_judgment) %>%
  summarize(k = sum(response), n = n()) %>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         low  = qbeta(.025, a, b),
         high = qbeta(.975, a, b),
         MAP_h = (a-1)/(a+b-2),
         mean = a / (a + b)) %>% 
  ungroup() %>%
  mutate(truth_judgment = factor(truth_judgment, levels = truth_judgment[order(MAP_h)]))

true_MAP <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "t")[[1,"MAP_h"]]
true_low <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "t")[[1,"low"]]
true_high <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "t")[[1,"high"]]

false_MAP <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "f")[[1,"MAP_h"]]
false_low <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "f")[[1,"low"]]
false_high <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "f")[[1,"high"]]

uncertain_MAP <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"MAP_h"]]
uncertain_low <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"low"]]
uncertain_high <- filter(d.gen.endorse.manipulation.check.bayes, truth_judgment == "i")[[1,"high"]]

As a manipulation check, the first author assigned an \emph{a priori} truth-judgment (true/false/indeterminate) to each stimulus item.
As one would expect, there were substantial differencesin empirical endorsements: true generics were almost universally endorsed (Maximum A-Posteriori estimate and 95\% credible interval of endorsement probability: $`r true_MAP` [`r true_low`, `r true_high`])$;
indeterminate generics were agreed with \emph{less} likely than chance ($`r uncertain_MAP` [`r uncertain_low`, `r uncertain_high`])$) but substantially more than false generics  ($`r false_MAP` [`r false_low`, `r false_high`])$).

In addition to these categorical differences between our thirty generic statements, we find a contiuum of endorsement values (Figure \ref{fig:generics-endorsement-figure}).
Such a continuum of judgments is already evidence against any theory that only predicts whether a generic statement is true or false.
Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, unendorsed completely, and all shades in between.
